---
title: "String_practice"
format: html
editor: visual
---
ok using tools adins to get this in 
```{r}
rm(list = ls())

pacman::p_load("tidyverse")
alarm_report <- data.frame(
  stringsAsFactors = FALSE,
              date = c("2020-03-14", "2020-03-15", "2020-04-10", "2020-04-18"),
          building = c("Engineering-North",
                       "Bren Hall","Engineering-South","Engr-North"),
     alarm_message = c("10:02am -- HVAC system down, facilities management alerted",
                       "8:24am -- Elevator North out of service",
                       "12:41am -- Fire alarm, UCSB fire responded and cleared",
                       "9:58pm -- Campus point emergency siren, UCPD responded")
)
```

Ok. We have these tasks:
1. Replace the “Engr” with “Engineering” in the building column
2. Separate the building column into two separate columns, building and wing, separated at the dash
3. Only keep observations with the word “responded” in the alarm_message column
4. Separate the message time from the rest of the message by separating at --
5.Convert the date column to a Date class using lubridate

#1
```{r}
alarm_report <-  alarm_report %>% 
  mutate(building = str_replace(building,pattern = "Engineering", replacement = "Engr"))
```

#2
```{r}
alarm_report <- alarm_report %>% 
  separate(col = building, into = c("building", "wing"), sep = "-")
```
#3
```{r}
alarm_report <- alarm_report %>% 
  filter(str_detect(alarm_message,"responded"))
```

#4
```{r}
alarm_report <- alarm_report %>% 
  separate(col = alarm_message, into = c("time", "alarm_message"), sep = "--")
```

#5
```{r}
alarm_report <- alarm_report %>% 
  mutate(date = ymd(date))
```
Nice
